Covariate analysis of MSSM reprocessed counts (with CQN normalisation and covariates adjusted)

### 2017-07-01 code/Rmd/MSSM_REPROCESSED.Rmd
Added MSSM 90+ ages

@@

METADATA <- full_join(METADATA_TECH, METADATA_CLINICAL) %>%
  inner_join(METADATA.PICARD)

@@

METADATA <- METADATA %>%
  filter(!is.na(BrainRegion.Diagnosis), !is.na(PMI), !is.na(RIN))
```

@@

Genes that are differentially expressed at an FDR <= 0.05 are
```{r diff.exp, fig.height=6, fig.width=15}
# Get design matrix
COVARIATES.tmp = COVARIATES %>%
  tidyr::separate(BrainRegion.Diagnosis, c('BrainRegion', 'Diagnosis'), sep = '\\.') %>%
  dplyr::mutate(BrainRegion = factor(BrainRegion))
DESIGN = getDesignMatrix(COVARIATES.tmp[, c('BrainRegion', postAdjustCovars), drop = F], Intercept = F)
ind = grep('BrainRegion', colnames(DESIGN$design))
DESIGN$design[,ind] = DESIGN$design[,ind] * as.numeric(COVARIATES.tmp[,'CDR'])
colnames(DESIGN$design)[ind] = paste0(colnames(DESIGN$design),'.CDR')
DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]

@@

p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
p = p + scale_color_manual(values = c('green','grey','red')) + theme(legend.position = 'top')
p = p + facet_grid(Comparison+.~BrainRegion, scales = 'free')
p
```

@@

DE = DE %>% 
  rbindlist(idcol = 'Comparison') %>%
  dplyr::mutate(Comparison = gsub('BrainRegion.Diagnosis','',Comparison),
                Study = 'MSSM',
                Direction = logFC/abs(logFC),
                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
                Direction = as.character(Direction)) %>%
  tidyr::separate(Comparison, c('from.state','to.state'), sep = '-') %>%
  tidyr::separate(from.state, c('BrainRegion','reference'), sep = '\\.') %>%
  tidyr::separate(to.state, c('BrainRegion','against'), sep = '\\.') %>%
  tidyr::unite(Comparison, reference, against, sep = '-') %>%
  left_join(GENE.PARAM %>%
              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
              unique())
DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'

@@

p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
p = p + scale_color_manual(values = c('green','grey','red')) + theme(legend.position='top')
p = p + facet_grid(BrainRegion+.~Comparison, scales = 'fixed')
p
```

@@

### SVA Adjustments for eQTL analysis
Conditioned on primary variable (BrainRegion.Diagnosis) and identified covariates estimate surrogate variables using SVA package
```{r sva.adjust}
# Get (null) design matrix
MODEL0 = DESIGN$design[,-grep(primaryVariable[2],colnames(DESIGN$design))] # Get null model by removing variable of interest
MODEL0 = MODEL0[,linColumnFinder(MODEL0)$indepCols]
MODEL1 = DESIGN$design
MODEL1 = MODEL1[,linColumnFinder(MODEL1)$indepCols]

@@

# Code
CODE <- Folder(name = "MSSM Reprocessed RNASeq (Normalised)", parentId = parentId)
annotations(CODE) = all.annotations
CODE <- synStore(CODE)

# Store covariates
COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
write.table(COVARIATES, file = 'MSSM_FP_STG_PHG_IFG_Covariates.tsv', sep = '\t', row.names=F, quote=F)
COV_OBJ = File('MSSM_FP_STG_PHG_IFG_Covariates.tsv', name = 'Covariates', parentId = CODE$properties$id)
annotations(COV_OBJ) = annotations(CODE)
annotations(COV_OBJ)$dataSubType = 'covariates'
COV_OBJ = synStore(COV_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)

@@

# Store design matrix
MODEL1 %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'MSSM_FP_STG_PHG_IFG_Design.tsv', sep = '\t', row.names=F, quote=F)
DM_OBJ = File('MSSM_FP_STG_PHG_IFG_Design.tsv', name = 'Design Matrix', parentId = CODE$properties$id)
annotations(DM_OBJ) = annotations(CODE)
annotations(DM_OBJ)$dataSubType = 'designMatrix'
DM_OBJ = synStore(DM_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

@@

# Store differential expression results
write.table(DE, file = 'MSSM_FP_STG_PHG_IFG_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('MSSM_FP_STG_PHG_IFG_DiffExpression.tsv', 
                name = 'Differential Expression Results (BrainRegion.Diagnosis)', 
                parentId = CODE$properties$id)
annotations(DEXP_OBJ) = annotations(CODE)
annotations(DEXP_OBJ)$dataSubType = 'diffExp'
DEXP_OBJ = synStore(DEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
stopCluster(cl)
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Surrogate Variables                        |  `r SURR_OBJ$properties$id`      |
|  Residual Expression (for eQTL)             |  `r eEXP_OBJ$properties$id`      |
|  Residual Expression (for network analysis) |  `r nEXP_OBJ$properties$id`      |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |

>>>>

# Get 90+ age
METADATA_AGE_ID = 'syn10156693'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_AGE_ID
METADATA_AGE <- read.table(synGet(METADATA_AGE_ID)@filePath, sep='\t', header=T) %>%
  dplyr::rename(individualIdentifier = BBid)

@@

METADATA <- dplyr::full_join(METADATA_TECH, METADATA_CLINICAL) %>%
  dplyr::inner_join(METADATA.PICARD) %>%
  dplyr::select(-AOD) %>%
  dplyr::left_join(METADATA_AGE)

@@

METADATA <- METADATA %>%
  filter(!is.na(BrainRegion.Diagnosis), !is.na(PMI), !is.na(RIN))

# Fix RIN values for some samples (Based on email conversation with Minghui May 22 2017)
FIX.RIN = c(hB_RNA_12312_resequenced = 3.9,
            hB_RNA_12342 = 3.9,
            hB_RNA_12352 = 4.2,
            hB_RNA_9191 = 5,
            hB_RNA_12262_resequenced = 5.2,
            hB_RNA_9216 = 5.7,
            hB_RNA_12272_resequenced = 5.8,
            hB_RNA_12382 = 5.8, 
            hB_RNA_13359 = 6.4)
rownames(METADATA) = METADATA$sampleIdentifier
METADATA[names(FIX.RIN),'RIN'] = FIX.RIN

METADATA = METADATA %>%
  dplyr::filter(RIN >= 5)
```

@@

Genes that are differentially expressed at an FDR <= 0.05 are
```{r diff.exp, fig.height=6, fig.width=15}
# Get design matrix
COVARIATES.tmp = COVARIATES %>%
  tidyr::separate(BrainRegion.Diagnosis, c('BrainRegion', 'Diagnosis'), sep = '\\.') %>%
  dplyr::mutate(BrainRegion = factor(BrainRegion))

DESIGN = getDesignMatrix(COVARIATES.tmp[, c('BrainRegion', postAdjustCovars), drop = F], Intercept = F)
ind = grep('BrainRegion', colnames(DESIGN$design))
DESIGN$design[,ind] = DESIGN$design[,ind] * as.numeric(COVARIATES.tmp[,'CDR'])
colnames(DESIGN$design)[ind] = paste0(colnames(DESIGN$design),'.CDR')
DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]

@@

p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
p = p + scale_color_manual(values = c('green','grey','red')) + theme(legend.position = 'top')
p = p + facet_grid(Comparison+.~BrainRegion, scales = 'free')
p

all.diff.exp = list(CDR = DE)
all.fit = list(CDR = FIT)
```

@@

DE = DE %>% 
  rbindlist(idcol = 'Comparison') %>%
  dplyr::mutate(Comparison = gsub('BrainRegion.Diagnosis','',Comparison),
                Study = 'MSSM',
                Direction = logFC/abs(logFC),
                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
                Direction = as.character(Direction)) %>%
  tidyr::separate(Comparison, c('from.state','to.state'), sep = '-') %>%
  tidyr::separate(from.state, c('BrainRegion','reference'), sep = '\\.') %>%
  tidyr::separate(to.state, c('BrainRegion1','against'), sep = '\\.') %>%
  dplyr::mutate(Comparison = paste(reference, against, sep = '-')) %>%
  dplyr::select(-BrainRegion1) %>%
  left_join(GENE.PARAM %>%
              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
              unique())
DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'

@@

p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
p = p + scale_color_manual(values = c('green','grey','red')) + theme(legend.position='top')
p = p + facet_grid(BrainRegion+.~Comparison, scales = 'fixed')
p

all.diff.exp = c(all.diff.exp, list(Diagnosis = DE))
all.fit = c(all.fit, list(Diagnosis = FIT))
```

@@

### Differential expression analysis (with BrainRegion.Diagnosis and Gender)
Differential expression is performed on the BrainRegion.Diagnosis x Gender variable by controlling for covariates identified above

Genes that are differentially expressed at an FDR <= 0.05 and folde change of 1.2 are
```{r diff.exp2, fig.height=15, fig.width=13}
## Modeling Diagnosis, msex and age_death conjointly
COVARIATES$BrainRegion.Diagnosis.SEX = paste(COVARIATES$BrainRegion.Diagnosis, 
                                             factor(COVARIATES$SEX, labels = c('F' = 'FEMALE', 'M' = 'MALE')), 
                                             sep = '.') %>% factor

# Get design matrix
DESIGN = getDesignMatrix(COVARIATES[, c('BrainRegion.Diagnosis.SEX', setdiff(postAdjustCovars, 'SEX')), drop = F], Intercept = F)
DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]

# Fit contrast
cntr = c('BrainRegion.Diagnosis.SEXIFG.AD.MALE-BrainRegion.Diagnosis.SEXIFG.CONTROL.MALE',
         'BrainRegion.Diagnosis.SEXIFG.AD.FEMALE-BrainRegion.Diagnosis.SEXIFG.CONTROL.FEMALE',
         '0.5*BrainRegion.Diagnosis.SEXIFG.AD.MALE+0.5*BrainRegion.Diagnosis.SEXIFG.AD.FEMALE
         -0.5*BrainRegion.Diagnosis.SEXIFG.CONTROL.MALE-0.5*BrainRegion.Diagnosis.SEXIFG.CONTROL.FEMALE',
         '0.5*BrainRegion.Diagnosis.SEXIFG.AD.FEMALE+0.5*BrainRegion.Diagnosis.SEXIFG.CONTROL.FEMALE
         -0.5*BrainRegion.Diagnosis.SEXIFG.AD.MALE-0.5*BrainRegion.Diagnosis.SEXIFG.CONTROL.FEMALE',
         '0.5*BrainRegion.Diagnosis.SEXIFG.AD.FEMALE-0.5*BrainRegion.Diagnosis.SEXIFG.CONTROL.FEMALE
         -0.5*BrainRegion.Diagnosis.SEXIFG.AD.MALE+0.5*BrainRegion.Diagnosis.SEXIFG.CONTROL.MALE',
         'BrainRegion.Diagnosis.SEXFP.AD.MALE-BrainRegion.Diagnosis.SEXFP.CONTROL.MALE',
         'BrainRegion.Diagnosis.SEXFP.AD.FEMALE-BrainRegion.Diagnosis.SEXFP.CONTROL.FEMALE',
         '0.5*BrainRegion.Diagnosis.SEXFP.AD.MALE+0.5*BrainRegion.Diagnosis.SEXFP.AD.FEMALE
         -0.5*BrainRegion.Diagnosis.SEXFP.CONTROL.MALE-0.5*BrainRegion.Diagnosis.SEXFP.CONTROL.FEMALE',
         '0.5*BrainRegion.Diagnosis.SEXFP.AD.FEMALE+0.5*BrainRegion.Diagnosis.SEXFP.CONTROL.FEMALE
         -0.5*BrainRegion.Diagnosis.SEXFP.AD.MALE-0.5*BrainRegion.Diagnosis.SEXFP.CONTROL.FEMALE',
         '0.5*BrainRegion.Diagnosis.SEXFP.AD.FEMALE-0.5*BrainRegion.Diagnosis.SEXFP.CONTROL.FEMALE
         -0.5*BrainRegion.Diagnosis.SEXFP.AD.MALE+0.5*BrainRegion.Diagnosis.SEXFP.CONTROL.MALE',
         'BrainRegion.Diagnosis.SEXPHG.AD.MALE-BrainRegion.Diagnosis.SEXPHG.CONTROL.MALE',
         'BrainRegion.Diagnosis.SEXPHG.AD.FEMALE-BrainRegion.Diagnosis.SEXPHG.CONTROL.FEMALE',
         '0.5*BrainRegion.Diagnosis.SEXPHG.AD.MALE+0.5*BrainRegion.Diagnosis.SEXPHG.AD.FEMALE
         -0.5*BrainRegion.Diagnosis.SEXPHG.CONTROL.MALE-0.5*BrainRegion.Diagnosis.SEXPHG.CONTROL.FEMALE',
         '0.5*BrainRegion.Diagnosis.SEXPHG.AD.FEMALE+0.5*BrainRegion.Diagnosis.SEXPHG.CONTROL.FEMALE
         -0.5*BrainRegion.Diagnosis.SEXPHG.AD.MALE-0.5*BrainRegion.Diagnosis.SEXPHG.CONTROL.FEMALE',
         '0.5*BrainRegion.Diagnosis.SEXPHG.AD.FEMALE-0.5*BrainRegion.Diagnosis.SEXPHG.CONTROL.FEMALE
         -0.5*BrainRegion.Diagnosis.SEXPHG.AD.MALE+0.5*BrainRegion.Diagnosis.SEXPHG.CONTROL.MALE',
         'BrainRegion.Diagnosis.SEXSTG.AD.MALE-BrainRegion.Diagnosis.SEXSTG.CONTROL.MALE',
         'BrainRegion.Diagnosis.SEXSTG.AD.FEMALE-BrainRegion.Diagnosis.SEXSTG.CONTROL.FEMALE',
         '0.5*BrainRegion.Diagnosis.SEXSTG.AD.MALE+0.5*BrainRegion.Diagnosis.SEXSTG.AD.FEMALE
         -0.5*BrainRegion.Diagnosis.SEXSTG.CONTROL.MALE-0.5*BrainRegion.Diagnosis.SEXSTG.CONTROL.FEMALE',
         '0.5*BrainRegion.Diagnosis.SEXSTG.AD.FEMALE+0.5*BrainRegion.Diagnosis.SEXSTG.CONTROL.FEMALE
         -0.5*BrainRegion.Diagnosis.SEXSTG.AD.MALE-0.5*BrainRegion.Diagnosis.SEXSTG.CONTROL.FEMALE',
         '0.5*BrainRegion.Diagnosis.SEXSTG.AD.FEMALE-0.5*BrainRegion.Diagnosis.SEXSTG.CONTROL.FEMALE
         -0.5*BrainRegion.Diagnosis.SEXSTG.AD.MALE+0.5*BrainRegion.Diagnosis.SEXSTG.CONTROL.MALE')
contrast = makeContrasts(contrasts=cntr,
                         levels = colnames(FIT$coefficients))
colnames(contrast) = c('IFG.AD.MALE-IFG.CONTROL.MALE',
                       'IFG.AD.FEMALE-IFG.CONTROL.FEMALE',
                       'IFG.AD.ALL-IFG.CONTROL.ALL',
                       'IFG.ALL.FEMALE-IFG.ALL.MALE',
                       'IFG.ALL.ALL-IFG.ALL.ALL',
                       'FP.AD.MALE-FP.CONTROL.MALE',
                       'FP.AD.FEMALE-FP.CONTROL.FEMALE',
                       'FP.AD.ALL-FP.CONTROL.ALL',
                       'FP.ALL.FEMALE-FP.ALL.MALE',
                       'FP.ALL.ALL-FP.ALL.ALL',
                       'PHG.AD.MALE-PHG.CONTROL.MALE',
                       'PHG.AD.FEMALE-PHG.CONTROL.FEMALE',
                       'PHG.AD.ALL-PHG.CONTROL.ALL',
                       'PHG.ALL.FEMALE-PHG.ALL.MALE',
                       'PHG.ALL.ALL-PHG.ALL.ALL',
                       'STG.AD.MALE-STG.CONTROL.MALE',
                       'STG.AD.FEMALE-STG.CONTROL.FEMALE',
                       'STG.AD.ALL-STG.CONTROL.ALL',
                       'STG.ALL.FEMALE-STG.ALL.MALE',
                       'STG.ALL.ALL-STG.ALL.ALL')

FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)

# Get differnetial expression
DE = lapply(1:dim(contrast)[2], function(i, FIT){
  topTable(FIT, coef=i, number = 50000, confint = T) %>%
    rownameToFirstColumn('ensembl_gene_id')
}, FIT.CONTR)
names(DE) = colnames(contrast)

DE = DE %>% 
  rbindlist(idcol = 'Comparison') %>%
  dplyr::mutate(Comparison = gsub('BrainRegion.Diagnosis','',Comparison),
                Study = 'MSSM',
                Direction = logFC/abs(logFC),
                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
                Direction = as.character(Direction)) %>%
  left_join(GENE.PARAM %>%
              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
              unique())
DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'

tmp = DE %>%
  dplyr::select(ensembl_gene_id, Comparison, Direction) %>%
  group_by(Comparison, Direction) %>%
  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
  spread(Direction, FDR_0_05_FC_1.2) 
kable(tmp)

all.diff.exp = c(all.diff.exp, list(Diagnosis.SEX = DE))
all.fit = c(all.fit, list(Diagnosis.SEX = FIT))
```

### Differential expression analysis (with BrainRegion.Diagnosis and AOD)
Differential expression is performed on the BrainRegion.Diagnosis x AOD variable by controlling for covariates identified above

Genes that are differentially expressed at an FDR <= 0.05 and folde change of 1.2 are
```{r diff.exp3, fig.height=15, fig.width=13}
# Get design matrix
DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[2], setdiff(postAdjustCovars, 'AOD')), drop = F], Intercept = F)
ind = grep('Diagnosis', colnames(DESIGN$design))
DESIGN$design[,ind] = DESIGN$design[,ind] * COVARIATES[rownames(DESIGN$design),'AOD']
DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
colnames(DESIGN$design)[ind] = gsub('BrainRegion.Diagnosis', '', paste0(colnames(DESIGN$design)[ind], '.AOD'))

# Fit contrast
cntr = c("FP.AD.AOD-FP.CONTROL.AOD",
         "0.5*FP.AD.AOD+0.5*FP.CONTROL.AOD",
         "IFG.AD.AOD-IFG.CONTROL.AOD",
         "0.5*IFG.AD.AOD+0.5*IFG.CONTROL.AOD",
         "PHG.AD.AOD-PHG.CONTROL.AOD",
         "0.5*PHG.AD.AOD+0.5*PHG.CONTROL.AOD",
         "STG.AD.AOD-STG.CONTROL.AOD",
         "0.5*STG.AD.AOD+0.5*STG.CONTROL.AOD")
contrast = makeContrasts(contrasts=cntr,
                         levels = colnames(FIT$coefficients))
colnames(contrast) = c("FP.AD.AOD-FP.CONTROL.AOD",
                       "FP.ALL.AOD",
                       "IFG.AD.AOD-IFG.CONTROL.AOD",
                       "IFG.ALL.AOD",
                       "PHG.AD.AOD-PHG.CONTROL.AOD",
                       "PHG.ALL.AOD",
                       "STG.AD.AOD-STG.CONTROL.AOD",
                       "STG.ALL.AOD")
FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)

# Get differnetial expression
DE = lapply(1:dim(contrast)[2], function(i, FIT){
  topTable(FIT, coef=i, number = 50000, confint = T) %>%
    rownameToFirstColumn('ensembl_gene_id')
}, FIT.CONTR)
names(DE) = colnames(contrast)

DE = DE %>% 
  rbindlist(idcol = 'Comparison') %>%
  dplyr::mutate(Comparison = gsub('BrainRegion.Diagnosis','',Comparison),
                Study = 'MSSM',
                Direction = logFC/abs(logFC),
                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
                Direction = as.character(Direction)) %>%
  left_join(GENE.PARAM %>%
              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
              unique())
DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'

tmp = DE %>%
  dplyr::select(ensembl_gene_id, Comparison, Direction) %>%
  group_by(Comparison, Direction) %>%
  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
  spread(Direction, FDR_0_05_FC_1.2) 
kable(tmp)

all.diff.exp = c(all.diff.exp, list(Diagnosis.AOD = DE))
all.fit = c(all.fit, list(Diagnosis.AOD = FIT))
```

### SVA Adjustments for eQTL analysis
Conditioned on primary variable (BrainRegion.Diagnosis) and identified covariates estimate surrogate variables using SVA package
```{r sva.adjust}
# Get design matrix
DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[2], postAdjustCovars), drop = F], Intercept = F)
DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]

# Get (null) design matrix
MODEL0 = DESIGN$design[,-grep(primaryVariable[2],colnames(DESIGN$design))] # Get null model by removing variable of interest
MODEL0 = MODEL0[,linColumnFinder(MODEL0)$indepCols]
MODEL1 = DESIGN$design
MODEL1 = MODEL1[,linColumnFinder(MODEL1)$indepCols]

@@

# Function to change entity ACL (also creates new acls if it doesn't exist)
synChangeEntityACL <- function(id, new.racl){
  tryCatch({ 
    # If old acl exist update
    old.acl = synGetEntityACL(id)
    old.acl@resourceAccess = new.racl
    synUpdateEntityACL(old.acl)
  }, error = function(e){ 
    # If not create a new acl
    new.acl = AccessControlList(id = id, resourceAccess = new.racl)
    synCreateEntityACL(new.acl)
  })
}

# Create new resource acls
new.racl = ResourceAccess(principalId = '3319864', 
                          accessType = c('UPDATE', 'CHANGE_SETTINGS', 'DELETE', 'READ', 
                                         'DOWNLOAD', 'MODERATE', 'CREATE', 'CHANGE_PERMISSIONS')) %>%
  ResourceAccessList() %>%
  synapseClient::append(ResourceAccess(principalId = '274008', 
                                       accessType = c('UPDATE', 'CHANGE_SETTINGS', 'DELETE', 'READ', 
                                                      'DOWNLOAD', 'MODERATE', 'CREATE', 'CHANGE_PERMISSIONS'))) %>%
  synapseClient::append(ResourceAccess(principalId = '273995', 
                                       accessType = c('UPDATE', 'CHANGE_SETTINGS', 'DELETE', 'READ', 
                                                      'DOWNLOAD', 'MODERATE', 'CREATE', 'CHANGE_PERMISSIONS'))) %>%
  synapseClient::append(ResourceAccess(principalId = '3359054', 
                                       accessType = c('READ', 'DOWNLOAD')))

# Code
CODE <- Folder(name = "MSSM Reprocessed RNASeq (Normalised)", parentId = parentId)
annotations(CODE) = all.annotations
CODE <- synStore(CODE)
synChangeEntityACL(CODE@properties$id, new.racl)

# Store covariates
COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
write.table(COVARIATES, file = 'MSSM_FP_STG_PHG_IFG_Covariates.tsv', sep = '\t', row.names=F, quote=F)
COV_OBJ = File('MSSM_FP_STG_PHG_IFG_Covariates.tsv', name = 'Covariates', parentId = CODE$properties$id)
annotations(COV_OBJ) = annotations(CODE)
annotations(COV_OBJ)$dataSubType = 'covariates'
COV_OBJ = synStore(COV_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
synChangeEntityACL(COV_OBJ@properties$id, new.racl)

@@

# Store design matrix
MODEL1 %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'MSSM_FP_STG_PHG_IFG_Design.tsv', sep = '\t', row.names=F, quote=F)
DM_OBJ = File('MSSM_FP_STG_PHG_IFG_Design.tsv', name = 'Design Matrix', parentId = CODE$properties$id)
annotations(DM_OBJ) = annotations(CODE)
annotations(DM_OBJ)$dataSubType = 'designMatrix'
DM_OBJ = synStore(DM_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
synChangeEntityACL(DM_OBJ@properties$id, new.racl)

@@

# Store differential expression results
rbindlist(all.diff.exp, use.names = T, fill = T, idcol = 'Model') %>%
  write.table(file = 'MSSM_FP_STG_PHG_IFG_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('MSSM_FP_STG_PHG_IFG_DiffExpression.tsv', name = 'Differential Expression Results (cogdx)', 
                parentId = CODE$properties$id)
annotations(DEXP_OBJ) = annotations(CODE)
annotations(DEXP_OBJ)$dataSubType = 'diffExp'
DEXP_OBJ = synStore(DEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store all differential expression models
save(all.fit, file = 'MSSM_FP_STG_PHG_IFG_Models.RData')
FIT_OBJ = File('MSSM_FP_STG_PHG_IFG_Models.RData', 
               name = 'All Limma Models',
               parentId = CODE$properties$id)
annotations(FIT_OBJ) = annotations(CODE)
annotations(FIT_OBJ)$dataSubType = 'modelFits'
FIT_OBJ = synStore(FIT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
synChangeEntityACL(FIT_OBJ@properties$id, new.racl)

# Delete folder acl
synDeleteEntityACL(CODE@properties$id)
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Surrogate Variables                        |  `r SURR_OBJ$properties$id`      |
|  Residual Expression (for eQTL)             |  `r eEXP_OBJ$properties$id`      |
|  Residual Expression (for network analysis) |  `r nEXP_OBJ$properties$id`      |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |
